TITLE

### 2017-09-23 paper/paper.tex
dataset

\section{Introduction}
Introduction content

\section{Data}
\subsection{Data Preprocessing}

>>>>

\section{Introduction}
\subsection{Motivation \& Background}
intro
\subsection{Related work}

\section{Data}
\subsection{Data origin \& structure}
The data set was created at a sleep laboratory \textbf{(the name of the lab?)} in Canada and kindly shared with us for the purpose of this project. The researchers in the laboratory analyse and model brain activity, with the use of Electoencephalography (EEG). EEG is a noninvasive method to record electrical activity of the brain, by placing electrodes along the scalp. We received data from one experiment which was conducted in the laboratory and focused on modeling dream and sleep activity and correlating it with sleep reports. The participants were asked to come to the lab, perform a virtual tennis game, or spatial navigation task, or both and then to go to sleep. After a short period of time, the participants were waken up and asked to verbally describe what they dreamt about. In some session types, the full night sleeps were additionally recorded. For this particular experiment, 22-channel EEG setup was applied, with the sampling rate of 128 samples per second, and the electrodes were customized to the participants according to the International 10-20 system, as can be seen in the figure 1.
\begin{figure}
	\centering
	\includegraphics[scale=0.1]{eeg}
	\caption{International 10-20 EEG placement system}
\end{figure}

All of the EEG data we received was already cleaned, so no additional filtering, or artifact rejection was needed to be performed. An example of the EEG data before preprocessing can be seen in figure 2.  For each of the 26 subjects who participated in the experiment, 3 different groups of data were provided: dream reports, mental rehearsals and verbal reports.  Dream reports contained EEG data during the short naps, mental rehearsals contained EEG data of when the participants were asked to repeat the same task they did in their minds (just to think about doing the task without actually doing it). Verbal reports were texts with the description of a dream provided by the participants after waking up. Each instance in the data was annotated with a label of the session and task type (tennis, spatial navigation, or both).
\begin{figure}
	\centering
	\includegraphics[scale=0.2]{eeg_ex}
	\caption{The sample of EEG from dream reports from one of the participants. EEG traces (horizontal: time in seconds; vertical: channel locations).}
\end{figure}

\subsection{Data Preprocessing}
